\section{Hardware and Software}
	The main product shall take the form of an ``Android app'' - a self 
	contained program running on an Android mobile device. This is what the 
	user will directly interact with. Our product will also require a central 
	server in order to function. The Android app shall be able to transfer 
	information to and from this sever.
	\subsection{Android Application}
		\subsubsection{Hardware}
			The device provided for testing the Android app is a HTC Desire C, 
			and the application should perform well on similar devices. The 
			relevant hardware capabilities of the Desire C are listed
			below\cite{htcdesirex}:

			\begin{itemize}
				\item Screen Resolution: 320 x 480 pixels
				\item Processor Speed: 600MHz
				\item Memory: 512MB
				\item SD Card Storage: 4GB +
				\item Battery Life: 10 - 20 hours of active use
				\item Internal GPS Antenna
			\end{itemize}

			\noindent
			The app is unlikely to require more capable hardware than what is 
			provided by the device because any intensive processing of data 
			can be offset to the central server. The most that the device will 
			need to handle is some trivial real-time graphical operations, and 
			for that the hardware is more than adequate. Memory should not be 
			a concern because the device has a relatively large amount for a 
			hand-held device, and this product will not require excessive 
			amounts of data to be stored. The app should not exhaust the 
			battery supply of the device to a prohibitive extent, and some 
			effort should be made during development to limit the usage of 
			battery draining resources. The product requires the ability to 
			find its current position using a GPS system, which is an ability 
			of the testing device. This device is considered a very basic
			model, and the majority of handsets in circulation are at least as
			capable. If an application functions well on the Desire C, it will
			function well on most devices.
		\subsubsection{Software}
			The application will be written in the programming language Java 
			using the development environment Eclipse, and will target the 
			Android operating system version 4.0 as a minimum as specified by 
			the client.

			Java will be used because it is the language the application 
			developers are most proficient in, and Eclipse was chosen for its 
			superior support for developing Android applications using the
			Android Developer Tools plugin.
	\subsection{Central Server}
		\subsubsection{Hardware}
			The central server program will reside on a conventional computer, 
			and because this one machine will handle all client requests it 
			will need much more advanced hardware than the mobile devices. 
			This server shall have internet connectivity in order to 
			communicate with the Android app clients. The server will also 
			need to be almost constantly active, with downtime only occurring 
			at times of the day when few clients will want to connect. The 
			machine running the server requires a large upload bandwidth in 
			order to service many clients in a small time frame, and this 
			should be complemented by a high enough CPU and memory access 
			speed to reduce the processing time of client requests. A lower 
			bandwidth can be compensated for by reducing the size of data 
			being sent to clients. The server should have enough free storage 
			space to allow for expansion of the product to cover more area of 
			the world. At a minimum, the server must have at least two
			processor cores to utilize multi-threading in the server software,
			2 GB of memory to be able to process a lot of data simultaneously 
			and also support the operating system, 16GB of available storage
			space to hold account and game data.

		\subsubsection{Software}
			The server will be written in the programming language C$\sharp$, 
			and built on the .NET Framework version 4.5 using the Visual 
			Studio 2012 development environment. C$\sharp$ was chosen for its 
			superior performance relative to Java, and because it is the 
			language the primary server developer is most experienced with.
			Visual Studio 2012 will be used for its support of .NET Framework
			4.5, and many tools to aid development.

	\subsection{Website}
		\subsubsection{Hardware}
			The web server will need to be hosted on the same machine as the
			game server to allow rapid transferral of data between them. This
			means the server will need the same hardware capabilities.

		\subsubsection{Software}
			The web server software will need to serve HTML pages with dynamic
			content pulled from the game server's data. Because the game server
			is also servicing HTML requests, they should be merged into one
			program. This means the software requirements are the same as for
			the central server.

			For clients accessing the website, they will need a web browser
			that supports the HTML 5 Canvas element. This includes the latest
			versions of Chromium, Firefox, Opera, Safari and Internet Explorer.
			We will be using Canvas to draw game related graphics.
