\documentclass[a4paper]{article}

\usepackage{lipsum}
\usepackage{fullpage}
\usepackage{hyperref}

\begin{document}
	\section{Hardware and Software}
		\subsection{Hardware}
			The main product shall take the form of an ``Android app'' - a self contained program running on an Android mobile device. This is what the user will directly interact with. Our product will also require a central server in order to function. The Android app shall be able to transfer information to and from this sever.

			\subsubsection{Android Application}
				The device provided for testing the Android app is a HTC Desire X, and the application should perform well on similar devices. The relevant hardware capabilities of the Desire X are listed below\cite{htcdesirex}:

				\begin{itemize}
					\item Screen Resolution: 800 x 480 pixels
					\item Processor Speed: 1GHz
					\item Memory: 768MB
					\item SD Card Storage: 4GB +
					\item Battery Life: 10 - 20 hours of active use
					\item Internal GPS Antenna
				\end{itemize}

				\noindent
				The app is unlikely to require more capable hardware than what is provided by the device because any intensive processing of data can be offset to the central server. The most that the device will need to handle is some trivial real-time graphical operations, and for that the hardware is more than adequate. Memory should not be a concern because the device has a very large amount. The app should not exhaust the battery supply of the device to a prohibitive extent, and some effort should be made during development to limit the usage of battery draining resources. The product requires the ability to find its current position using a GPS system, which is an ability of the testing device.
		\subsection{Software}

	\begin{thebibliography}{9}
		\bibitem{htcdesirex}
			HTC Corporation,
			\emph{HTC Desire X Specs}.
			November 2012

			\url{http://www.htc.com/www/smartphones/htc-desire-x/#specs}
	\end{thebibliography}

\end{document}
